An Automatic Verification Framework for Software Configurations

### 2016-05-09 OSDI/motiv.tex
better wording

In the above, 104857600 represents the integer value of 100 megabytes. The idea is to give the user
a warning that their value falls outside of a range considered normal and to prompt the  
appropriate adjustments.

>>>>

In the above, 104857600 represents the integer value of 100 megabytes. The idea is to output
a warning to the user that her value falls outside of a range considered normal, so that she
can make the appropriate adjustment to the value herself.
